Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

\extraspacing {\underline{\em Example 5.6.}} It is clear from Figure~\ref{fig:hv:type2:ex}(d) that $\contained_{R_2}(h_3^*)$ has rectangles $\beta_3, \beta_2$, $\beta_1$, sorted in descending order of their right boundaries' x-coordinates. Consider $\bm{t}_2 = (\alpha, h_3', v_1)$ and $\bm{t}_3 = (\alpha, h_3', v_2)$. Segment $h_3^*$ is the minimal segment of $h_3'$. As stated in Lemma~\ref{lmm:hv:type2:contained-h*}, both $\contained_{R_2}(\bm{t}_2) = \set{\beta_1, \beta_2, \beta_3}$ and $\contained_{R_2}(\bm{t}_3) = \set{\beta_1}$ are prefixes of the sorted order of $\contained_{R_2}(h_3^*)$. Regarding $h_2^*$, it is the minimal segment of $h_2'$, and $\contained_{R_2}(h_2^*)$ contains only  $\beta_1$. For $\bm{t}_1 = (\alpha, h_2', v_1)$, $\contained_{R_2}(\bm{t}_1) = \set{\beta_1}$ is a (trivial) prefix of $\contained_{R_2}(h_2^*)$, as is consistent with the lemma.
\done

>>>>

\extraspacing {\underline{\em Example 5.6.}} It is clear from Figure~\ref{fig:hv:type2:ex}(d) that $\contained_{R_2}(h_3^*)$ has rectangles $\beta_3, \beta_2$, $\beta_1$, sorted in descending order of their right boundaries' x-coordinates. Consider $\bm{t}_2 = (\alpha, h_3', v_1)$ and $\bm{t}_3 = (\alpha, h_3', v_2)$. Segment $h_3^*$ is the minimal segment of $h_3'$. As stated in Lemma~\ref{lmm:hv:type2:contained-h*}, both $\contained_{R_2}(\bm{t}_2) = \set{\beta_1, \beta_2, \beta_3}$ and $\contained_{R_2}(\bm{t}_3) = \set{\beta_1}$ are prefixes of the sorted order of $\contained_{R_2}(h_3^*)$. Regarding $h_2^*$, it is the minimal segment of $h_2'$, and $\contained_{R_2}(h_2^*)$ contains only  $\beta_1$. For $\bm{t}_1 = (\alpha, h_2', v_1)$, $\contained_{R_2}(\bm{t}_1) = \set{\beta_1}$ is a (trivial) prefix of $\contained_{R_2}(h_2^*)$, as is also consistent with the lemma.
\done
